\newcommand{\maxN}{10^6} %
\newcommand{\maxM}{10^6} %
\newcommand{\trm}{\textrm} %
\newcommand {\animN}{$\trm{animal}_\trm{n}\,$} %
\problemname{Genefinderx9000}
Bobby is a biology researcher with a great interest in genetics. \\
He loves to wander out in the wild collecting new DNA samples for his database which he later uses for his research. \\
He has to find exact matches to genetic patterns in the DNA of the animals he has collected.
However, it takes Bobby multiple weeks to manually check which animals contain the exact sequences of DNA he is looking for, so he could use a little help. \\
Your task is to write a program that Bobby can use to find all the animals that contain a specific DNA sequence in his database.
\begin{equation}
\label{1}
\alpha =  \{\trm{'A','C','T','G'}\}
\end{equation}
\subsection*{Input}
The first line of input has a single integer $\trm{I}$ the number of animals in the database. \\
Each of the following $\trm{I}$ lines depicts the genes of \animN as an unique non-empty string. \\
The combined length of the $\trm{I}$ animals is promised to never exceed $\maxN$.
\\
Following the $\trm{I}$ lines is a single integer $\trm{K}$.
The next $\trm{K}$ lines depicts a $\trm{query}_\trm{k}$ as an unique non-empty string. The total length of the $\trm{K}$ queries is promised to never exceed $\maxM$. \\ \\
Both the $\trm{I}$ animals and the $\trm{K}$ queries consist exclusively of characters from the gene alphabet $\alpha$ (see equation 1). 

\subsection*{Output}
Given a database of animal genes you are to output the answer to each query on a single line. \\ 
For simplicity the animals are numbered from $0$ to $I-1$. \\ 
The answer to $\trm{query}_\trm{k}$ should be given as $Z \,\, z_0 \,\cdots \,\trm{z}_{\trm{Z}-1}$, where $Z$ denotes the count\\
of animals containing the \trm{k}'th sequence 
and $\trm{z}_0 \,\cdots \,\trm{z}_{\trm{Z}-1}$ is a space-separated integer set of the $Z$ animals. \\ 
The $\trm{Z}$ animals should be given in ascending order such that 
$\trm{animal}_\trm{j} \leq \trm{z}_{\trm{j}+1}$ for all $\trm{z} \, \epsilon \, \{\,0\,,\cdots\,,\trm{Z}-1\,\}$. 
